\bf Visualizing probability distributions across bivariate nonlinear temporal granularities

### 2020-02-13 main.tex
re-compile after addressing Rob's comments till Section 2

Linear time granularities respect the linear progression of time such as hours, days, weeks and months, and non-repeating. One of the first attempts to characterize these granularities is due to \citet{Bettini1998-ed}. However, the definitions and rules defined are inadequate for describing nonlinear or repeating granularities. Hence, there is a need to define some new nonlinear time granularities, that can be useful in visualizations. Nonlinear time granularities can be circular, quasi-circular or aperiodic. Examples of circular granularities are hour of the day and day of the week; an examples of a quasi-circular granularty is day of the month; examples of aperiodic granularities are public holidays and school holidays.

@@

\todo[inline]{Give an example}

@@

\todo[inline]{Give an example}

@@

\todo[inline]{What does "full-integer" mean?}

@@

\todo[inline]{What does this last phrase mean?}

@@

\begin{verbatim}
#> # A tsibble: 1,450,232 x 3 [30m] <UTC>
#> # Key:       customer_id [50]
#>    customer_id reading_datetime    general_supply_kwh
#>    <chr>       <dttm>                           <dbl>
#>  1 10006414    2012-02-10 08:00:00              0.141
#>  2 10006414    2012-02-10 08:30:00              0.088
#>  3 10006414    2012-02-10 09:00:00              0.078
#>  4 10006414    2012-02-10 09:30:00              0.151
#>  5 10006414    2012-02-10 10:00:00              0.146
#>  6 10006414    2012-02-10 10:30:00              0.077
#>  7 10006414    2012-02-10 11:00:00              0.052
#>  8 10006414    2012-02-10 11:30:00              0.055
#>  9 10006414    2012-02-10 12:00:00              0.055
#> 10 10006414    2012-02-10 12:30:00              0.252
#> # ... with 1,450,222 more rows
\end{verbatim}

@@

From the search list, we found six cyclic granularities for which we would like to derive insights of energy behavior. Given the data structure \textless{}\(C1\) \(C2\), \texttt{general\_supply\_kwh}\textgreater, each of those six cyclic granularities can either be mapped to x-axis or to facet. Thus the problem is equivalent to taking 2 granularities at a time from 6, which essentially is equivalent to having 30 data subsets for visualisation. However, harmony/clash pairs can be identified among those 30 possibilities to determine feasibility of plotting any pairs together. We are left with 13 harmonies pair, each of which can be plotted together to look at the energy behavior from different perspectives.

@@

\begin{verbatim}
#> The chosen granularities are harmonies 
#>  
#> Recommended plots are: violin lv quantile boxplot 
#>  
#> Number of observations are homogenous across facets 
#>  
#> Number of observations are homogenous within facets 
#>  
#> Cross tabulation of granularities : 
#>  
#> # A tibble: 24 x 3
#>    hour_day Weekday Weekend
#>    <fct>      <dbl>   <dbl>
#>  1 0            910     366
#>  2 1            908     366
#>  3 2            909     366
#>  4 3            910     366
#>  5 4            910     366
#>  6 5            910     366
#>  7 6            909     366
#>  8 7            908     366
#>  9 8            908     366
#> 10 9            908     366
#> # ... with 14 more rows
\end{verbatim}

>>>>

Linear time granularities respect the linear progression of time such as hours, days, weeks and months, and non-repeating. One of the first attempts to characterize these granularities is due to \citet{Bettini1998-ed}. However, the definitions and rules defined are inadequate for describing nonlinear or repeating granularities. Hence, there is a need to define some new nonlinear time granularities, that can be useful in visualizations. Nonlinear time granularities can be circular, quasi-circular or aperiodic. Examples of circular granularities are hour of the day and day of the week; an examples of a quasi-circular granularity is day of the month; examples of aperiodic granularities are public holidays and school holidays.

@@

{\centering \includegraphics[width=1\linewidth]{Figs/groups_periodically}

\caption{Linear granularity $B$ groups periodically into linear granularity $G$ with $P = 5$ and $R = 2$, alternating between combining 2 and 3 granules of $B$.}\label{fig:group-periodical}
\end{figure}

@@

{\centering \includegraphics[width=1\linewidth]{Figs/quasi_groups_periodically}

\caption{Linear granularity $B$ groups quasi-periodically into linear granularity $G$ with $P = 5$ and $R = 2$, alternating between combining 2 and 3 granules of $B$ with $E1$ as the exception.}\label{fig:quasi-group-periodical}
\end{figure}

\textbf{Example}: Example showing periodic and quasi-periodic linear granularities are displayed in \autoref{fig:group-periodical} and \autoref{fig:quasi-group-periodical} respectively. Each granule is represented by a box. In these figures, the granules that overlap share elements from the underlying time domain. In both of these cases, each granule of \(G\) is made up of two and three granules of \(B\) alternately. So the period is \(P = 5\) and number of granules of \(G\) in each period is given by \(R=2\). The only difference in \autoref{fig:quasi-group-periodical} is that there is an exception after the first granule of \(G\) which consists of one granule of \(B\). Except for this exception \(E1\), \(B\) groups periodically into \(G\).

@@

\todo[inline]{What does "full-integer" mean? It might be the case that we do not always
have integers as the label sets of granularities. A full-integer labeled granularities are defined in definition 2 since labels coincide with indices. These labels can be an
arbitrary subset of (possibly non contiguous) integers and could be used to identify granules. The author has introduced the definition of "labeled granularity" in @Ning2002-tf which could be added after definition of linear granularity to clarify this. }

@@

\todo[inline]{What does this last phrase mean? - if  the time horizon is such that it starts from the 15th second of a day, then doing repeated operations of grouping might result in a granule of "resultant" granularity day or week, which is different from a time-stamped day or week. Could be phrased better or deleted.}

When the granules for second and minutes are arranged, the first granule of seconds and minutes granules should that overlap share elements from the underlying time domain\}

@@

\begin{verbatim}
#> # A tsibble: 1,450,232 x 3 [30m] <UTC>
#> # Key:       customer_id [50]
#>    customer_id reading_datetime    general_supply_kwh
#>    <chr>       <dttm>                           <dbl>
#>  1 10006414    2012-02-10 08:00:00              0.141
#>  2 10006414    2012-02-10 08:30:00              0.088
#>  3 10006414    2012-02-10 09:00:00              0.078
#>  4 10006414    2012-02-10 09:30:00              0.151
#>  5 10006414    2012-02-10 10:00:00              0.146
#>  6 10006414    2012-02-10 10:30:00              0.077
#>  7 10006414    2012-02-10 11:00:00              0.052
#>  8 10006414    2012-02-10 11:30:00              0.055
#>  9 10006414    2012-02-10 12:00:00              0.055
#> 10 10006414    2012-02-10 12:30:00              0.252
#> # … with 1,450,222 more rows
\end{verbatim}

@@

From the search list, we found six cyclic granularities for which we would like to derive insights of energy behavior. Given the data structure \textless{}\(C1\) \(C2\), \texttt{general\_supply\_kwh}\textgreater{}, each of those six cyclic granularities can either be mapped to x-axis or to facet. Thus the problem is equivalent to taking 2 granularities at a time from 6, which essentially is equivalent to having 30 data subsets for visualisation. However, harmony/clash pairs can be identified among those 30 possibilities to determine feasibility of plotting any pairs together. We are left with 13 harmonies pair, each of which can be plotted together to look at the energy behavior from different perspectives.

@@

\begin{verbatim}
#> The chosen granularities are harmonies 
#>  
#> Recommended plots are: violin lv quantile boxplot 
#>  
#> Number of observations are homogenous across facets 
#>  
#> Number of observations are homogenous within facets 
#>  
#> Cross tabulation of granularities : 
#>  
#> # A tibble: 24 x 3
#>    hour_day Weekday Weekend
#>    <fct>      <dbl>   <dbl>
#>  1 0            910     366
#>  2 1            908     366
#>  3 2            909     366
#>  4 3            910     366
#>  5 4            910     366
#>  6 5            910     366
#>  7 6            909     366
#>  8 7            908     366
#>  9 8            908     366
#> 10 9            908     366
#> # … with 14 more rows
\end{verbatim}
